---
title: "Comparison of Coronavirus infection and deaths per country: how far behind Italy are we?"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
The goal of this script is to compare the chronology of infection/death caused per country and use Italy to predict the situation in other countries, notably in France.

```{r, load libraries, include=F}
library(ggplot2)
library(gplots)
```

```{r, load dataset, echo=F}
# infections
i <- read.table("csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Confirmed.csv", sep=",", h=T)
# deaths
d <- read.table("csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Deaths.csv", sep=",", h=T)
# Recoveries
r <- read.table("csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Recovered.csv", sep=",", h=T)

dates <- as.Date(gsub(".","/",gsub("X","",colnames(d)[6:ncol(d)]), fixed=T), "%m/%d/%y")
dates <- as.Date(format(dates,"%d/%m/%y"),"%d/%m/%y")
```

Let's compare the contagion and death curves between countries.
```{r, prep function for plotting, include=F}
plot_dataset <- function(table, title, date_indexes=date_indexes){
  color_country <- c(Italy="red", France="blue", Germany="black", Spain="orange")

# Plot points
  plot_country <- function(country, date_indexes=date_indexes){
    sel <- which(table$Country.Region==country)
    points(dates[date_indexes-5],table[sel,date_indexes], xlab="Date", ylab="Deaths", type="b", pch=20, cex=0.6, col=color_country[country]) #, main=paste(d$Province.State[i], d$Country.Region[i])
# axis
  }
  plot_countries <- function(countries, date_indexes=date_indexes){
    sels <- which(d$Country.Region%in%countries)
    ymax=max(table[sels,date_indexes])
    par(xaxt="n")
    plot(dates[date_indexes-5],table[1,date_indexes], xlab="Date", ylab=title, type="n", pch=20, cex=0.6, ylim=c(0,ymax), main=title)
    lablist<-dates[date_indexes-5]
    axis(1, at=seq(1, length(dates[date_indexes-5]), by=1), labels = FALSE)
    text(dates[date_indexes-5], par("usr")[3]-ymax/15, labels = lablist, srt = 90, pos = 1, xpd = TRUE, cex=0.5)
    for (country in countries){
     plot_country(country, date_indexes=date_indexes)
    }
   legend("topleft", legend=countries, col=color_country[countries], pch=20, text.col=color_country[countries])
  }

  plot_countries(c("Italy","France","Germany", "Spain"), date_indexes=date_indexes)
}
```

```{r, plot coronavirus graphs for countries, echo=F}
plot_dataset(table=i, title="Infections", date_indexes=19:ncol(d))
plot_dataset(table=d, title="Deaths", date_indexes=19:ncol(d))
```

France and Italy have (roughly) the same number of inhabitants, so the absolute numbers of cases can be directly compared. France seems to be X days behind Italy. If we delay Italy by X days, how do the curves compare between countries?

```{r, Delay Italy to mimic France}


```

